Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-03-26 Scripts/Initial_Analysis.Rmd
fixing nan bugs

 eez_summary <- spp %>% 
   group_by(eez_name,time_step) %>% 
   summarise(
      min_spp = min(mean_spp),
     max_spp = max(mean_spp),
     sd_spp = sd(mean_spp,na.rm=T), # for some weird reason it wont work if the order is fliped
     mean_spp = mean(mean_spp,na.rm=T)
   ) %>% 
   select(eez_name:max_spp,mean_spp,sd_spp)

@@

 proportion_change <- eez %>% 
   gather("variable","value",min_spp:sd_spp) %>% 
   spread(time_step,value) %>% 
   mutate_at(vars(
     "per_mid" = mid,
     "per_end" = n_end),
            funs(round((((.-historical)/.))*100,2))
   )

@@

Restuls <- PropChange(taxon_list[1:2])

write.csv(Results,
          "Clean_Results.csv")

@@

>>>>

 eez_summary <- spp %>% 
   group_by(eez_name,time_step) %>% 
   summarise(
     n_spp = n(),
     min_spp = min(mean_spp,na.rm=T),
     max_spp = max(mean_spp,na.rm=T),
     sd_spp = sd(mean_spp,na.rm=T), # for some weird reason it wont work if the order is fliped
     mean_spp = mean(mean_spp,na.rm=T)
   ) %>% 
   select(eez_name:max_spp,mean_spp,sd_spp)

@@

 proportion_change <- eez %>% 
   gather("variable","value",n_spp:sd_spp) %>% 
   spread(time_step,value) %>% 
   mutate_at(vars(
     "per_mid" = mid,
     "per_end" = n_end),
            funs(round((((.-historical)/.))*100,2))
   )

@@

results <- PropChange(taxon_list)

# write_csv(Results,
#           "Clean_Results.csv")

clean_results <- fread(paste(result_path,"Clean_Results.csv",sep=""))
View(clean_results)

@@

## Figure 1. Change Map

```{r figure_one, eval = T, echo =F}

# Load SAU shapefile name and paths

# The path
path_world <- paste(data_path,"Spatial_Data/SAU_Shapefile/",sep="")

# The File
fnam_world <- "SAUEEZ_July2015.shp"

# Load it!
World_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name)

# View(unique(World_sf$eez_name))
